\documentclass[12pt, letterpaper]{article}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{enumitem}
\onehalfspace

\title{Team 3: Jon Behling & Matt Kousiry}
\begin{document}
\begin{center}
\textbf{\underline{Team 3: Jon Behling \& Matt Kousiry}}
\end{center}
\textbf{Project Title: }Pet the Dog!
\\
\textbf{Short Description: }Our project revolves around giving digital love and affection to Bruce, everyone’s favorite golden retriever. Users will be welcomed to a login page that will track their individual progress. Once logged in and verified (or account created), they will be receive a wonderful photo of Bruce with a button to digitally pet him. Each pet is tracked and can be publicly displayed on a results page. Here, users can see who has given Bruce the most pets. Administrators for the website can generate reports on the number of user accounts that have been created, individual email addresses for contact (so their prize can be distributed of course), and other crucial information. 
\\
\textbf{Page Requirements and Functionality: }
\begin{enumerate}
    \item Home Page with a welcome message, competition description, links to login or create an account – Always Visible
    \item An “About Bruce” Page.
    \item Linked Page to search for users that give the highest amount of love to Bruce – publicly visible
    \item Basic Login/Logout functionality
    \item HTML Form w/PHP Sign Up Script
    \item Administrator-Only access to account logs (i.e. usernames, passwords, emails, etc.)
    \item Server-Side Scripting to log \# number of clicks made to “pet bruce”
    \item Client-Side Scripting to set cookies for individual users to track \# of pets made by each individual account
\end{enumerate}
\textbf{Project Plan:}
\begin{itemize}[label={-}]
    \item Milestone 1: H	ome Page, About Bruce, Create Account Portion
    \item Jon:  Create Account Portion
    \item Matt:  Home Page
    \item Collab: About Bruce
    \item Milestone 2: Admin-Logs, List of Results
    \item Jon: List of Results
    \item Matt: Admin-Logs
    \item Milestone 3: Search functionality, Server, Client Side Scripting
    \item Jon:  Search functionality
    \item Matt: Client Side Scripting
    \item Collab: Message Board, Server
\end{itemize}

Note that if one of us finishes our parts and the other is struggling, we will work together to solve the issue as we see fit.
\end{document}